Flabby and injective objects in toposes

### 2022-02-14 paper-flabby-objects.tex
to do

\XXX{If Zorn's lemma is not available but E is localic, ... is at least true
if E is compact.}

@@

FUTURE:

* Does "flabby sheaves are acyclic on all locales" imply Zorn?

* quasicompact/spectral case

>>>>

\begin{rem}We can dispose the reliance on Zorn's lemma in
Scholium~\ref{scholium:exact-as-presheaves} if instead~$\E$ is compact. This is
because XXX ... finitely many local preimages ... patch together ... by the
following internal observation ...
\end{rem}

@@

TO DO:
* enough injectives employing only Zorn
* first names?

FUTURE:
* Does "flabby sheaves are acyclic on all locales" imply Zorn?
* quasicompact/spectral case
